---
title: "Titanic ML visualization"
author: "Ajay Rahul"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

These visualizations are for the Kaggle's Titanic prediction competiton. The datasets are download from the site itself.Details about the competiton and datasets can be seen here https://www.kaggle.com/c/titanic.


#### 1.) Installing the necessary packages

The initial data was processed in Spark using Linear Regression to find the prediction Model written in Scala. To view the code, visit https://github.com/AjayRahul/Machine-Learning-Scala-and-R/blob/2f556caaa077b7d08786f232e7aa5358e494f14c/TitianicKaggle.scala

```{r cars, warning=FALSE}
suppressMessages(library('dplyr'))
suppressMessages(library('ggplot2'))
suppressMessages(library('ggthemes'))
suppressMessages(library('plyr'))
suppressMessages(library('randomForest'))
suppressMessages(library('corrplot'))

```

#### 2.) Importing the Dataset


```{r pressure}
train <- read.csv("C:/Users/Lenovo/Desktop/Kaggle/Titanic/train.csv", stringsAsFactors = F)
test <- read.csv("C:/Users/Lenovo/Desktop/Kaggle/Titanic/test.csv", stringsAsFactors = F)
```

#### 3.) Combining both the two data into a single table

```{r r1}
fullDs <- bind_rows(train, test)
```
#### 4.) Viewing the data summary and it's structure

```{r r2, echo=TRUE}
 summary(fullDs)
```

```{r r3} 
str(fullDs)
```

#### 5.) Viewing the Age versus Survived visualization
```{r r4, echo=TRUE, warning=FALSE}
 ggplot(fullDs[1:891,], aes(Age,fill = factor(Survived)))+geom_histogram(bins = 40)+xlab("Age")+scale_fill_discrete(name = " ", labels = c("Survived", "Dead"))+ggtitle("Age vs Survived")+ylab("Number of person survived")
```

#### 6.) Viewing the Sex versus Survived visualization
```{r r5, echo=TRUE, warning=FALSE}

 ggplot(fullDs[1:891,], aes(Sex,fill = factor(Survived)))+geom_bar(stat = "count", position = "dodge")+xlab("Sex")+scale_fill_discrete(name = " " , labels = c("Survived", "Dead"))+ggtitle("Deatils on Survival on the basis of Gender")+ylab("Number of person survived")
```

```{r r6, echo=TRUE, warning=FALSE}
ggplot(fullDs[1:891,], aes(x=Age, y=Sex))+geom_jitter(aes(colour = factor(Survived)))+labs(x="Age", title=" ")+scale_x_continuous(name="Age", limits = c(0,81))+scale_fill_discrete(labels=c("Survived", "Dead"))
```






##### Here the legend "0" states "Alive" and 1 states "Dead"